Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
statistics in paper

Our results suggest that viewing incorrect approximate data biases participant responses about correct data for certain types of questions.
For question type 1, how many, the expected bias had no impact on participant response $(t)$.

@@

>>>>

Our results suggest that viewing incorrect approximate data biases participant responses about correct data for certain types of questions.
For question type 1, how many, the expected bias had no impact on participant response ($F_{1, 75}=2.702, p=0.104$).
For question types 2 and 3 (comparison and inclusion), the expected bias had a significant effect on participant response ($F_{1, 238}=45.214, p<0.0001$ for type 2, $F_{1, 75}=118.438, p<0.0001$ for type 3).

We note that although the p-value for type 1 questions is above $\alpha=0.05$, it approaches significance.
We plan to conduct a power analysis for our next iteration of the study and likely scale up participation.
With more data, we expect this effect would be statistically significant.
That said, the effect for question type 1 was smaller than the other question types.
This aligns with the finding that the error for this type of question was lower overall.

@@

Our results fail to reject the hypothesis that visualization type impacts the bias.
Condition did not have a significant main effect for any question type ($F_{2,75}=1.174, p=0.315$, $F_{2,238}=0.776, p=0.462$, and $F_{2,75}=0.061, p=0.941$ for types 1, 2, and 3 respectively).
We only observed an interaction effect question type 3 ($F_{2,75}=3.665, p=0.030$), but post-hoc tests proved inconclusive as to the directionality of the effect.

We believe the individual variance between participants exceeded any differences between visualizations.
